DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-08-14 manuscript/manuscript.Rmd
revisions

Deep learning has garnered increasing interest in recent years due to successful applications in many fields [@lecun2015deep] and has recently made its way into the loss reserving literature. @wuthrich2018neural augments the traditional chain ladder method with neural networks to incorporate claims features, and @gabrielli2018neural embeds the over-dispersed Poisson (ODP) model into a neural network.

@@

For comprehensive treatments of neural network mechanics and implementation, we refer the reader to @goodfellow2016deep and @chollet2018deep. In order to establish common terminology used in this paper, we present a brief overview in this section.

@@

We can then think of a neural network as a sequence of function compositions $f = f_L \circ f_{L-1} \circ \dots \circ f_1$ parameterized as $f(x; W^{[1]}, b^{[1]}, \dots, W^{[L]}, b^{[L]})$.

@@

\begin{equation}
\sigma(x) = \frac{1}{1 + \exp(-x)}\label{eq:eq1}.
\end{equation}
$W_h$, $W_r$, $W_u$, $b_h$, $b_r$, and $b_u$ are the appropriately sized weight matrices and biases to be learned.

@@

is used as the activation function for the fully connected layers, including both of the output layers.

@@

[^1]: https://github.com/kevinykuo/deeptriangle

>>>>

Deep learning has garnered increasing interest in recent years due to successful applications in many fields [@lecun2015deep] and has recently made its way into the loss reserving literature. @wuthrich2018neural augments the traditional chain ladder method with neural networks to incorporate claims features, @gabrielli2018individual utilizes neural networks to syntheisze claims data, and @gabrielli2018neural and @gabrielli2019neural embeds classical parametric loss reserving models into neural networks.

@@

For comprehensive treatments of neural network mechanics and implementation, we refer the reader to @goodfellow2016deep and @chollet2018deep. A more actuarially oriented discussion can be found in @wuthrich2019data. In order to establish common terminology used in this paper, we present a brief overview in this section.

@@

We can then think of a neural network as a sequence of function compositions $f = f_L \circ f_{L-1} \circ \dots \circ f_1$ parameterized as $f(x; W^{[1]}, b^{[1]}, \dots, W^{[L]}, b^{[L]})$. Here, it should be mentioned that the activation functions $g^{[t]}$ are chosen to be nonlinear, except for possibly in the output layer. These nonlinearities are key to the success of neural networks, because otherwise we would have a trivial composition of linear models.

@@

\begin{equation}
\sigma(x) = \frac{1}{1 + \exp(-x)}\label{eq:eq1}.
\end{equation}
$W_h$, $W_r$, $W_u$, $b_h$, $b_r$, and $b_u$ are the appropriately sized weight matrices and biases to be learned. Intuitively, the activations $h^{<t>}$ provide a way for the network to maintain state and "remember" values from early values of the input sequence. The values $\tilde{h}^{<t>}$ can be thought of as candidates to replace the current state, and $\Gamma_u^{<t>}$ determines the weighting between the previous state and the candidate state. We remark that although the GRU (and RNN in general) may seem opaque at first, they contain sequential instructions for updating weights just like vanilla feedforward neural networks (and can in fact be interpreted as such [@goodfellow2016deep]).

@@

is used as the activation function for the fully connected layers, including both of the output layers. We remark that this choice of output activation implies we only predict nonnegative cash flows, i.e. no recoveries. This assumption is reasonable for the dataset we use in our experiments, but may be modified to accommodate other use cases.

@@

[^1]: https://github.com/kasaai/deeptriangle
